---
title: "Minimal COVID-19 dashboard"
author: "Martin Chan"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: columns
    vertical_layout: fill
---

<style>                     
.navbar {
  background-color:#363636;
  
}
</style>   
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dashboard
=====================================

Column {data-width=300}
-----------------------------------------------------------------------

```{r message=FALSE, warning=FALSE, include=FALSE}  
#### Load packages ####
library(tidyverse)
library(flexdashboard)
library(dygraphs)
library(timetk)
library(here)


#### Load functions ####
source(here("Script", "Functions", "create_dt.R"))
source(here("Script", "Functions", "rgb2hex.R"))

#### Load datasets ####
df_confirmed <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv")
df_deaths <- read_csv("https://github.com/CSSEGISandData/COVID-19/raw/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Deaths.csv")
df_recovered <- read_csv("https://github.com/CSSEGISandData/COVID-19/raw/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Recovered.csv")

run_summary <- function(data, varname){
  data %>%
    select(-`Province/State`, -`Country/Region`, -Lat, -Long) %>%
    gather(Date, !!sym(varname)) %>%
    group_by(Date) %>%
    summarise(!!sym(varname) := sum(!!sym(varname)))
}

df_confirmed %>% run_summary(varname = "Confirms") -> summary_confirmed
df_deaths %>% run_summary(varname = "Deaths") -> summary_deaths
df_recovered %>% run_summary(varname = "Recovered") -> summary_recovered

list(summary_confirmed,
     summary_deaths,
     summary_recovered) %>%
  reduce(full_join, by = "Date") %>%
  mutate(N_Outcome = Deaths + Recovered) %>%
  mutate(FatalityRate = Deaths / N_Outcome) %>%
  mutate_at(vars(Date), ~lubridate::mdy(.)) -> output_data
```

### Total Global Confirms

```{r echo=FALSE}
summary_confirmed %>%
  summarise(Confirms = max(Confirms, na.rm = TRUE)) %>%
  pull(Confirms) -> n_confirms

n_confirms %>%
  valueBox(caption = "Total Global Confirms",
           icon = "fa-sort-up",
           color = rgb2hex(222,0,0))
```

### Total Global Deaths

```{r echo=FALSE}
summary_deaths %>%
  summarise(Deaths = max(Deaths, na.rm = TRUE)) %>%
  pull(Deaths) -> n_deaths

n_deaths %>%
  valueBox(caption = "Total Deaths",
           icon = "fa-sort-up",
           color = rgb2hex(77,69,48))
```

### Total Global Recovered

```{r echo=FALSE}
summary_recovered %>%
  summarise(Recovered = max(Recovered, na.rm = TRUE)) %>%
  pull(Recovered) -> n_recovered

n_recovered %>%
  valueBox(caption = "Total Recovered",
           icon = "fa-sort-up",
           color = rgb2hex(11,71,6))
```


### Fatality Rate

<!-- Calculated as a % of deaths over _total deaths_ plus _total recovered_. -->

```{r echo=FALSE}
output_data %>%
  arrange(desc(Date)) %>%
  slice(1) %>%
  pull(FatalityRate) -> n_fr

n_fr %>%
  surveytoolbox::as_percent() %>%
  valueBox(caption = "Fatality rate",
           icon = "fa-sort-up",
           color = rgb2hex(227,166,0))
```

Column {data-width=500} {.tabset}
-----------------------------------------------------------------------

### Fatality Rate

```{r echo=FALSE}
output_data %>%
  # ggplot(aes(x = Date, y = FatalityRate)) +
  # geom_line()
  timetk::tk_xts(select = c(N_Outcome, FatalityRate),
                 date_var = Date) %>%
  dygraph(main = "Outcomes and Fatality Rate") %>%
  dyAxis("y", label = "Fatality Rate") %>%
  dyAxis("y2", label = "Number of Confirmed Cases with Outcomes", independentTicks = TRUE) %>%
  dyAxis("x", label = "Date") %>%
  dySeries("N_Outcome", axis = "y2") %>%
  dyRangeSelector() %>%
  dyOptions(colors = c(rgb2hex(65,75,170),rgb2hex(128,128,128)),
            drawGrid = FALSE, fillGraph = TRUE) %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = TRUE)
```

### Table

```{r echo=FALSE}
output_data %>%
  arrange(Date) %>%
  create_dt() %>%
  DT::formatPercentage(c("FatalityRate"), 1)
```

Background
=====================================

### Background

Minimal COVID-19 (novel coronavirus) dashboard built using RMarkdown and flexdashboard

This is a minimal prototype to build COVID-19 dashboard using the {RMarkdown} and {flexdashboard} packages.

The data used to build the analysis is taken from the data repository for the 2019 Novel Coronavirus Visual Dashboard, operated by the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE). Their GitHub repo is linked [here](https://github.com/CSSEGISandData/COVID-19).

Other useful dashboards (by others) on COVID-19 can be found below:
- [Coronavirus COVID-19 Global Cases by Johns Hopkins CSSE](https://gisanddata.maps.arcgis.com/apps/opsdashboard/index.html#/bda7594740fd40299423467b48e9ecf6)
- [Novel Coronavirus Health Map](https://www.healthmap.org/wuhan/)
- [Coronavirus App](https://coronavirus.app/)

- [Link to this dashboard](https://raw.githack.com/martinctc/COVID-19-R/master/Script/covvirus_analysis_20200224.html)
- [Link to the GitHub repo](https://github.com/martinctc/COVID-19-R)