---
title: "Minimal COVID-19 dashboard"
author: "Martin Chan"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

<style>                     
.navbar {
  background-color:#363636;
  
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#### Load packages ####
library(tidyverse)
library(flexdashboard)
library(surveytoolbox)
library(dygraphs)
library(timetk)
library(here)
```

Dashboard
=====================================

```{r message=FALSE, warning=FALSE, include=FALSE}  
#### Load functions ####
source(here("Script", "Functions", "create_dt.R"))
source(here("Script", "Functions", "rgb2hex.R")) # Convert RGB to HEX
source(here("Script", "Functions", "run_summary.R")) # Summary analysis functions

#### Load datasets ####
df_confirmed <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")
df_deaths <- read_csv("https://github.com/CSSEGISandData/COVID-19/raw/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")
df_recovered <- read_csv("https://github.com/CSSEGISandData/COVID-19/raw/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv")

df_confirmed %>% run_summary(varname = "Confirms") -> summary_confirmed
df_deaths %>% run_summary(varname = "Deaths") -> summary_deaths
df_recovered %>% run_summary(varname = "Recovered") -> summary_recovered

list(summary_confirmed,
     summary_deaths,
     summary_recovered) %>%
  reduce(full_join, by = "Date") %>%
  mutate(N_Outcome = Deaths + Recovered) %>%
  mutate(FatalityRate = Deaths / N_Outcome) %>%
  mutate(GrossFatalityRate = Deaths / Confirms) %>%
  mutate_at(vars(Date), ~lubridate::mdy(.)) %>%
  arrange(Date) %>%
  drop_na() -> output_data

## Define date to be used throughout
output_data %>%
  pull(Date) %>%
  # lubridate::mdy() %>%
  max() -> today_date

```

```{r child=here::here("Script", "Chunks", "ValueBoxes.Rmd")}
```

```{r child=here::here("Script", "Chunks", "ValueBoxes2.Rmd")}
```



Column {data-width=500} {.tabset}
-----------------------------------------------------------------------

### Confirms, Recovers, and Deaths over time

```{r echo=FALSE}
output_data %>%
  timetk::tk_xts(select = c(Confirms, Deaths, Recovered),
                 date_var = Date) %>%
  dygraph(main = "Confirms, Recovers, and Deaths over time - Global") %>%
  dyAxis("y", label = "Number of people") %>%
  dyAxis("x", label = "Date") %>%
  dyRangeSelector() %>%
  dyOptions(colors = c(rgb2hex(65,75,170),rgb2hex(128,128,128)),
            drawGrid = FALSE, fillGraph = TRUE) %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = TRUE)
```


### Fatality Rate

```{r echo=FALSE}
output_data %>%
  # ggplot(aes(x = Date, y = FatalityRate)) +
  # geom_line()
  timetk::tk_xts(select = c(N_Outcome, FatalityRate),
                 date_var = Date) %>%
  dygraph(main = "Outcomes and Fatality Rate") %>%
  dyAxis("y", label = "Fatality Rate") %>%
  dyAxis("y2", label = "Number of Confirmed Cases with Outcomes", independentTicks = TRUE) %>%
  dyAxis("x", label = "Date") %>%
  dySeries("N_Outcome", axis = "y2") %>%
  dyRangeSelector() %>%
  dyOptions(colors = c(rgb2hex(65,75,170),rgb2hex(128,128,128)),
            drawGrid = FALSE, fillGraph = TRUE) %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = TRUE)
```

### New vs Total Confirms

```{r echo=FALSE}
output_data %>%
  arrange(Date) %>%
  mutate(New_cases = Confirms - lag(Confirms, 1)) %>%
  drop_na(New_cases) %>%
  timetk::tk_xts(select = c(Confirms, New_cases),
                 date_var = Date) %>%
  dygraph(main = "New vs Total Cases") %>%
  dyAxis("y", label = "Cumulative confirms") %>%
  dyAxis("y2", label = "New cases per day", independentTicks = TRUE) %>%
  dyAxis("x", label = "Date") %>%
  dySeries("New_cases", axis = "y2") %>%
  dyRangeSelector() %>%
  dyOptions(colors = c(rgb2hex(65,75,170),rgb2hex(128,128,128)),
            drawGrid = FALSE, fillGraph = TRUE) %>%
  dyHighlight(highlightCircleSize = 5,
              highlightSeriesBackgroundAlpha = 0.2,
              hideOnMouseOut = TRUE)
```

```{r child=here::here("Script", "Chunks", "DeepDive_UK.Rmd")}
```

```{r child=here::here("Script", "Chunks", "Tables.Rmd")}
```

Background
=====================================

### Background

Minimal COVID-19 (novel coronavirus) dashboard built using RMarkdown and flexdashboard

This is a minimal prototype to build COVID-19 dashboard using the {RMarkdown} and {flexdashboard} packages.

The data used to build the analysis is taken from the data repository for the 2019 Novel Coronavirus Visual Dashboard, operated by the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE). Their GitHub repo is linked [here](https://github.com/CSSEGISandData/COVID-19).

Other useful dashboards (by others) on COVID-19 can be found below:

- [Coronavirus COVID-19 Global Cases by Johns Hopkins CSSE](https://gisanddata.maps.arcgis.com/apps/opsdashboard/index.html#/bda7594740fd40299423467b48e9ecf6)
- [Novel Coronavirus Health Map](https://www.healthmap.org/wuhan/) 
- [Coronavirus App](https://coronavirus.app/) 

- [Link to this dashboard](https://raw.githack.com/martinctc/COVID-19-R/master/Script/covvirus_analysis_20200229.html)

- [Link to the GitHub repo](https://github.com/martinctc/COVID-19-R)